\documentclass[11pt,a4paper]{article}

% ============================================================
% Packages
% ============================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,left=0.68in,right=0.68in,top=0.70in,bottom=0.85in,
  includeheadfoot,headheight=14pt,footskip=24pt]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{booktabs,tabularx,array,adjustbox,xltabular,makecell,
  ragged2e,etoolbox,needspace,placeins,hyphenat,longtable}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{caption}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}

\hypersetup{colorlinks=true,linkcolor=blue!45!black,
  urlcolor=blue!45!black,citecolor=blue!45!black}

% ============================================================
% Layout
% ============================================================
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\raggedbottom
\sloppy
\emergencystretch=4em
\tolerance=9999
\hbadness=9999
\vfuzz=2pt
\hfuzz=1pt

\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=2pt,parsep=0pt}
\setlist[enumerate]{leftmargin=*,itemsep=2pt,topsep=2pt,parsep=0pt}

\setlength{\tabcolsep}{2.5pt}
\renewcommand{\arraystretch}{1.08}
\newcolumntype{Y}{>{\RaggedRight\arraybackslash\hspace{0pt}}X}
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash\hspace{0pt}}p{#1}}

\AtBeginEnvironment{xltabular}{%
  \scriptsize\setlength{\tabcolsep}{2.5pt}\renewcommand{\arraystretch}{1.08}}
\AtEndEnvironment{xltabular}{\normalsize}
\AtBeginEnvironment{longtable}{%
  \scriptsize\setlength{\tabcolsep}{2.5pt}\renewcommand{\arraystretch}{1.08}}
\AtEndEnvironment{longtable}{\normalsize}

\lstdefinestyle{code}{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  breakatwhitespace=false,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framesep=3pt,
  xleftmargin=0pt,
  xrightmargin=0pt,
  linewidth=\linewidth,
  rulecolor=\color{black!20},
  backgroundcolor=\color{black!2},
  aboveskip=4pt,
  belowskip=4pt
}
\lstset{style=code}

\pagestyle{fancy}
\fancyhf{}
\lhead{CEX Import Documentation}
\rhead{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0.3pt}

\title{\textbf{CEX Import Documentation}\\
\large Binance Historical Data and Live Order-Book Collector\\
for the AMM Thesis\\[4pt]
\normalsize Version 1.0 \quad|\quad May 2026}
\author{Arthur Gallo}
\date{May 2026}

\begin{document}
\maketitle
\thispagestyle{fancy}

\begin{abstract}
This document describes the centralised-exchange (CEX) raw-data import
module used for the AMM thesis. It records which Python script imports
which data object, the output folder structure, the raw file formats
and column definitions, the download and retry behaviour, the default
test parameters, the full historical import preset, and the connection
between imported CEX variables and AMM calibration objects.

All column descriptions, constants, formulas, status values, and
file-path conventions have been verified directly against the source
scripts (\texttt{cex\_config.py}, \texttt{binance\_download\_utils.py},
\texttt{main\_import\_cex.py}, \texttt{fetch\_binance\_klines.py},
\texttt{fetch\_binance\_agg\_trades.py},
\texttt{collect\_binance\_orderbook\_rest.py}).

The import module writes raw outputs to
\path{C:\Courses\thesis_AMM\data_raw\CEX\binance}. Cleaning,
resampling, merging with DEX data, and model-parameter estimation
are deferred to \path{C:\Courses\thesis_AMM\scripts\process_data\CEX}.
\end{abstract}

\tableofcontents
\newpage

% ============================================================
\section{Abbreviations and Terminology}
\label{sec:glossary}

\begin{xltabular}{\linewidth}{L{3.0cm}Y}
\toprule
\textbf{Term} & \textbf{Definition} \\
\midrule
CEX & Centralised exchange. An exchange in which a central operator
     maintains the order book and matches trades. \\
DEX & Decentralised exchange. An on-chain automated market maker. \\
AMM & Automated market maker. \\
ETH & Ether. The native asset of the Ethereum blockchain. On centralised
     exchanges, ETH balances are maintained internally and do not require
     ERC-20 wrapping. \\
WETH & Wrapped Ether. An ERC-20 token pegged 1:1 to ETH, used by Uniswap
      v3 on-chain. The symbol for the DEX pool is WETH/USDC; the
      corresponding CEX pair is ETH/USDC. \\
USDC & USD Coin. A USD-pegged ERC-20 stablecoin. \\
USDT & Tether. A USD-pegged stablecoin. \\
Kline & Candlestick. A summary of trading activity over a fixed interval:
        open, high, low, close prices, base volume, quote volume, and
        trade count. Also called a candle or OHLCV bar. \\
Agg trade & Aggregate trade. A Binance representation in which all raw
            fills from a single taker order executed at the same price and
            millisecond are compressed into one record. \\
OHLCV & Open, High, Low, Close, Volume. Standard candlestick fields. \\
VWAP & Volume-weighted average price: $\sum_i p_i q_i / \sum_i q_i$. \\
Basis point (bp) & One hundredth of one percent ($0.0001$). \\
NDJSON & Newline-delimited JSON. A file format where each line is one
         self-contained JSON object. \\
SHA-256 & A cryptographic hash function used here to fingerprint
          downloaded ZIP archives for integrity verification. \\
LVR & Loss-versus-rebalancing. A metric comparing AMM LP returns against
      a passive rebalancing strategy. \\
\bottomrule
\end{xltabular}

% ============================================================
\section{Purpose and Scope}
\label{sec:purpose}

The CEX import module collects publicly available Binance market data
needed to calibrate and validate the AMM thesis model. The DEX side of
the thesis is obtained from The Graph (Uniswap v3 event-level data,
documented separately). The CEX side provides an external reference
market for ETH prices, realised volatility, centralised-exchange volume,
trade counts, trade-size distributions, bid--ask spreads, and
order-book depth.

The key empirical comparison is between the Uniswap v3 WETH/USDC
price and the CEX reference ETH price:
\[
  d_t = \frac{p_t^{\mathrm{AMM}} - p_t^{*}}{p_t^{*}},
\]
where $p_t^{*}$ is constructed from the imported CEX data.

\noindent\textbf{What the module provides.}
\begin{itemize}
  \item Historical Binance klines (candlesticks) for ETHUSDC, ETHUSDT,
        and USDCUSDT at 1-minute and 5-minute intervals.
  \item Historical Binance aggregate trades for the same symbols.
  \item Prospective live order-book snapshots from the moment the
        collector is started.
\end{itemize}

\noindent\textbf{What the module does not provide.}
\begin{itemize}
  \item Historical full limit-order-book depth (not freely available
        in backfill form from Binance public data).
  \item Individual order submissions and cancellations.
  \item Private user identifiers or hidden liquidity.
  \item Trade-flow labels (arbitrage, market-making, noise flow).
  \item Merged DEX--CEX panels (deferred to processing).
\end{itemize}

\noindent\textbf{Why WETH/USDC versus ETH/USDC.} The Uniswap v3 pool
trades WETH on-chain because Ethereum smart contracts require the
ERC-20 wrapped form. Centralised exchanges record ETH balances
internally and do not need wrapping. The CEX benchmark therefore uses
the ETH/USDC and ETH/USDT symbols, which are economically equivalent
to WETH/USDC for the purpose of constructing $p_t^{*}$.

\noindent\textbf{Symbol coverage and period justification.}
Three symbols are used:

\begin{xltabular}{\linewidth}{L{2.6cm}L{3.2cm}Y}
\toprule
\textbf{Symbol} & \textbf{Pair} & \textbf{Justification} \\
\midrule
\texttt{ETHUSDC} & ETH priced in USDC & Direct USDC-denominated benchmark
  for the Uniswap v3 WETH/USDC pool. Available on Binance from a later
  date than ETHUSDT; missing periods return \texttt{missing\_404} in
  the manifest. \\
\texttt{ETHUSDT} & ETH priced in USDT & Longer benchmark available from
  2017. Required for the full 2022--2026 sample period when ETHUSDC
  is incomplete. \\
\texttt{USDCUSDT} & USDC priced in USDT & Stablecoin-basis correction
  pair. Used to construct a synthetic USDC-denominated ETH price:
  $p^{\mathrm{ETH/USDC}}_t \approx p^{\mathrm{ETH/USDT}}_t /
  p^{\mathrm{USDC/USDT}}_t$. \\
\bottomrule
\end{xltabular}

% ============================================================
\section{Project Folder Convention}
\label{sec:paths}

\begin{lstlisting}
C:\Courses\thesis_AMM\
    data_raw\
        CEX\
            binance\
    data_processed\
        CEX\
    scripts\
        import_data\
            CEX\
                cex_config.py
                binance_download_utils.py
                main_import_cex.py
                fetch_binance_klines.py
                fetch_binance_agg_trades.py
                collect_binance_orderbook_rest.py
        process_data\
            CEX\
    output\
        tables\
        figures\
    docs\
\end{lstlisting}

\noindent\textbf{Path resolution.}
\texttt{cex\_config.py} resolves the project root using
\texttt{Path(\_\_file\_\_).resolve().parents[3]}, which assumes the
script resides exactly three directory levels below the project root
(i.e.\ in \texttt{scripts\textbackslash import\_data\textbackslash
CEX\textbackslash}). Moving any script to a different depth will
silently write outputs to an incorrect location unless
\texttt{.parents[3]} is updated.

\noindent\textbf{Raw versus processed data.}
The raw folder (\texttt{data\_raw\textbackslash CEX\textbackslash
binance}) stores files as close as possible to the original Binance
format. No column names, values, or types are modified during import.
Conversion, resampling, and merging are deferred to
\texttt{scripts\textbackslash process\_data\textbackslash CEX}.

% ============================================================
\section{Script Inventory}
\label{sec:inventory}

\begin{xltabular}{\linewidth}{L{5.0cm}L{2.8cm}Y}
\toprule
\textbf{File} & \textbf{Role} & \textbf{Responsibility} \\
\midrule
\texttt{run\_cex.py} & Top-level runner &
  Recommended entry point. Located one directory above the CEX scripts
  (in \texttt{scripts\textbackslash import\_data\textbackslash}).
  Sets \texttt{PYTHONIOENCODING=utf-8} automatically, then invokes
  \texttt{main\_import\_cex.py --full-history}. Accepts
  \texttt{--orderbook} (enable live order-book collection) and
  \texttt{--overwrite} (re-download existing files). \\
\addlinespace
\texttt{cex\_config.py} & Shared configuration &
  Defines \texttt{PROJECT\_ROOT}, output paths, Binance endpoints,
  HTTP behaviour constants, and raw CSV column-name lists
  (\texttt{KLINE\_COLUMNS}, \texttt{AGG\_TRADE\_COLUMNS}) for use in
  downstream processing scripts. \\
\addlinespace
\texttt{binance\_download\_utils.py} & Download utilities &
  Provides period iterators, URL builder, local-path resolver,
  ZIP downloader with retry, CSV extractor, SHA-256 hasher,
  manifest writer, and the \texttt{DownloadResult} dataclass.
  All other scripts import from here. \\
\addlinespace
\texttt{main\_import\_cex.py} & Main controller &
  Core parameter file. Defines all user parameters and the
  full-history preset. Accepts command-line overrides. Calls kline,
  aggregate-trade, and order-book scripts. Invoked by
  \texttt{run\_cex.py} for the standard full-history import. \\
\addlinespace
\texttt{fetch\_binance\_klines.py} & Historical candles &
  Downloads Binance spot kline ZIP archives for specified symbols,
  intervals, date range, and granularity. Can be run directly. \\
\addlinespace
\texttt{fetch\_binance\_agg\_trades.py} & Historical aggregate trades &
  Downloads Binance spot aggregate-trade ZIP archives for specified
  symbols and periods. Can be run directly. \\
\addlinespace
\texttt{collect\_binance\_orderbook\_rest.py} & Live order-book
  collector &
  Polls the Binance REST depth endpoint at a configurable interval.
  Writes compact spread/depth CSV summaries and optional full
  NDJSON snapshots. Prospective only; no historical backfill. \\
\bottomrule
\end{xltabular}

% ============================================================
\section{Shared Configuration: \texttt{cex\_config.py}}
\label{sec:config}

\subsection{Paths and Endpoints}

\begin{xltabular}{\linewidth}{L{5.2cm}L{4.5cm}Y}
\toprule
\textbf{Name} & \textbf{Value} & \textbf{Description} \\
\midrule
\texttt{PROJECT\_ROOT} &
  \texttt{Path(\_\_file\_\_).resolve()} \newline \texttt{.parents[3]} &
  Resolved at import time. Points to
  \path{C:\Courses\thesis_AMM} when the script is in
  \texttt{scripts\textbackslash import\_data\textbackslash CEX}. \\
\texttt{DEFAULT\_OUTPUT\_ROOT} &
  \texttt{PROJECT\_ROOT / "data\_raw" / "CEX"} &
  General raw CEX data root. \\
\texttt{BINANCE\_OUTPUT\_ROOT} &
  \texttt{DEFAULT\_OUTPUT\_ROOT / "binance"} &
  Binance-specific raw data root; used as the default
  \texttt{output\_root} throughout all scripts. \\
\texttt{BINANCE\_PUBLIC\_DATA\_BASE\_URL} &
  \texttt{https://data.binance.vision/data} &
  Base URL for Binance Data Vision public ZIP archives. \\
\texttt{BINANCE\_SPOT\_API\_BASE\_URL} &
  \texttt{https://api.binance.com} &
  Base URL for the live Binance REST API (order-book endpoint). \\
\bottomrule
\end{xltabular}

\subsection{Download Behaviour Constants}

\begin{xltabular}{\linewidth}{L{5.2cm}L{2.0cm}Y}
\toprule
\textbf{Name} & \textbf{Value} & \textbf{Description} \\
\midrule
\texttt{REQUEST\_TIMEOUT\_SECONDS} & \texttt{60} &
  HTTP request timeout in seconds, applied to both the public-data
  downloader and the REST order-book fetcher. \\
\texttt{MAX\_RETRIES} & \texttt{3} &
  Maximum download attempts per file in \texttt{download\_zip}.
  The order-book \texttt{fetch\_depth} function also uses 3 retries
  (hard-coded in its signature default). \\
\texttt{RETRY\_SLEEP\_SECONDS} & \texttt{2.0} &
  Fixed pause between retry attempts in \texttt{download\_zip}.
  Not exponential: the wait is \texttt{RETRY\_SLEEP\_SECONDS}
  on every retry except the last. The order-book fetcher uses
  an independent hard-coded 2.0-second sleep between its retries. \\
\texttt{DEFAULT\_SLEEP\_BETWEEN\_ DOWNLOADS\_SECONDS} &
  \texttt{0.25} &
  Pause applied after each successful (or skipped) public-data
  file request. Applied unconditionally when \texttt{sleep\_seconds
  > 0}. \\
\bottomrule
\end{xltabular}

\subsection{Raw CSV Column-Name Lists}

Binance Data Vision CSV files are stored without a header row.
\texttt{cex\_config.py} provides two ordered lists of column names
for use in downstream processing scripts. The import scripts
themselves do not inject these names into the raw files.

\texttt{KLINE\_COLUMNS} (in order):
\texttt{open\_time\_ms},
\texttt{open},
\texttt{high},
\texttt{low},
\texttt{close},
\texttt{volume\_base},
\texttt{close\_time\_ms},
\texttt{quote\_asset\_volume},
\texttt{number\_of\_trades},
\texttt{taker\_buy\_base\_volume},
\texttt{taker\_buy\_quote\_volume},
\texttt{ignore}.

\texttt{AGG\_TRADE\_COLUMNS} (in order):
\texttt{agg\_trade\_id},
\texttt{price},
\texttt{quantity},
\texttt{first\_trade\_id},
\texttt{last\_trade\_id},
\texttt{transact\_time\_ms},
\texttt{is\_buyer\_maker},
\texttt{is\_best\_match}.

% ============================================================
\section{Download Utilities: \texttt{binance\_download\_utils.py}}
\label{sec:utils}

\subsection{The \texttt{DownloadResult} Dataclass}

Every call to \texttt{download\_one\_binance\_public\_file} returns a
frozen \texttt{DownloadResult} instance and appends one row to the
manifest. The fields are:

\begin{xltabular}{\linewidth}{L{3.8cm}L{2.6cm}Y}
\toprule
\textbf{Field} & \textbf{Type} & \textbf{Description} \\
\midrule
\texttt{exchange} & \texttt{str} &
  Always \texttt{"binance"}. \\
\texttt{market\_type} & \texttt{str} &
  Always \texttt{"spot"}. \\
\texttt{data\_type} & \texttt{str} &
  \texttt{"klines"} or \texttt{"aggTrades"}. \\
\texttt{symbol} & \texttt{str} &
  Upper-stripped symbol, e.g.\ \texttt{"ETHUSDC"}. \\
\texttt{interval} & \texttt{str} &
  Kline interval, e.g.\ \texttt{"1m"}. Empty string for aggTrades. \\
\texttt{granularity} & \texttt{str} &
  \texttt{"daily"} or \texttt{"monthly"}. \\
\texttt{period} & \texttt{str} &
  \texttt{YYYY-MM-DD} for daily; \texttt{YYYY-MM} for monthly. \\
\texttt{url} & \texttt{str} &
  Full remote URL requested. \\
\texttt{zip\_path} & \texttt{Path} &
  Local path of the ZIP archive. \\
\texttt{extracted\_dir} & \texttt{Optional[Path]} &
  Directory where CSV was extracted; \texttt{None} if extraction
  did not occur or no CSV member was found inside the ZIP. \\
\texttt{status} & \texttt{str} &
  See Section~\ref{sec:statuses}. \\
\texttt{bytes\_downloaded} & \texttt{int} &
  Bytes downloaded, or local file size when status is
  \texttt{exists}/\texttt{exists\_extracted}. Zero for
  \texttt{missing\_404} and \texttt{failed}. \\
\texttt{sha256} & \texttt{str} &
  SHA-256 hex digest of the local ZIP file. Computed after
  download or when status is \texttt{exists}. Empty string for
  \texttt{missing\_404} and \texttt{failed}. \\
\texttt{error} & \texttt{str} &
  Error message if applicable; empty string otherwise. \\
\bottomrule
\end{xltabular}

\subsection{Download Status Values}
\label{sec:statuses}

The \texttt{download\_zip} function returns one of four primitive
statuses (\texttt{downloaded}, \texttt{exists}, \texttt{missing\_404},
\texttt{failed}). The wrapper
\texttt{download\_one\_binance\_public\_file} then appends the suffix
\texttt{\_extracted} or \texttt{\_no\_csv} when applicable, and may
override to \texttt{failed\_extract}. The full set of possible
\texttt{status} values written to the manifest is:

\begin{xltabular}{\linewidth}{L{4.8cm}Y}
\toprule
\textbf{Status} & \textbf{Meaning} \\
\midrule
\texttt{downloaded} &
  ZIP downloaded successfully; extraction not requested
  (\texttt{extract=False}). \\
\texttt{downloaded\_extracted} &
  ZIP downloaded and at least one CSV member extracted. \\
\texttt{downloaded\_no\_csv} &
  ZIP downloaded but no member with a \texttt{.csv} extension
  was found inside. \\
\texttt{exists} &
  ZIP already present locally and non-empty; not re-downloaded
  (\texttt{overwrite=False}); extraction not requested. \\
\texttt{exists\_extracted} &
  ZIP already present; CSV files were available or extracted from it. \\
\texttt{missing\_404} &
  HTTP 404 received. Expected for symbol-period combinations that
  do not exist on Binance (e.g.\ ETHUSDC before the symbol launched).
  The 404 is not retried. \\
\texttt{failed} &
  All \texttt{MAX\_RETRIES} = 3 download attempts failed. The
  temporary \texttt{.tmp} file is deleted. \\
\texttt{failed\_extract} &
  Download or existence check succeeded, but an exception was
  raised during SHA-256 computation or CSV extraction. \\
\bottomrule
\end{xltabular}

\subsection{URL Construction}
\label{sec:urls}

\texttt{build\_data\_vision\_url} constructs Binance Data Vision URLs
of the following patterns:

\begin{lstlisting}
# klines (daily)
https://data.binance.vision/data/spot/daily/klines/<SYM>/<INT>/<SYM>-<INT>-<YYYY-MM-DD>.zip

# klines (monthly)
https://data.binance.vision/data/spot/monthly/klines/<SYM>/<INT>/<SYM>-<INT>-<YYYY-MM>.zip

# aggTrades (daily)
https://data.binance.vision/data/spot/daily/aggTrades/<SYM>/<SYM>-aggTrades-<YYYY-MM-DD>.zip

# aggTrades (monthly)
https://data.binance.vision/data/spot/monthly/aggTrades/<SYM>/<SYM>-aggTrades-<YYYY-MM>.zip
\end{lstlisting}

A non-empty \texttt{interval} is required for klines; passing an
empty string raises a \texttt{ValueError}. For aggTrades, the
\texttt{interval} parameter is ignored.

\subsection{Local Path Layout}
\label{sec:localpaths}

\texttt{local\_paths(output\_root, ...)} returns
\texttt{(zip\_path, extract\_dir)}. The paths follow this layout:

\begin{lstlisting}
# Extracted CSVs (output_root is data_raw\CEX\binance)
output_root\spot\<granularity>\klines\<SYM>\<INT>\
output_root\spot\<granularity>\aggTrades\<SYM>\

# ZIP archives
output_root\zip_archives\spot\<granularity>\klines\<SYM>\<INT>\
output_root\zip_archives\spot\<granularity>\aggTrades\<SYM>\
\end{lstlisting}

Note that the comment in \texttt{local\_paths} says
``\texttt{output\_root/binance/\ldots}'', but since
\texttt{output\_root} is already set to
\texttt{BINANCE\_OUTPUT\_ROOT} (which ends in \texttt{binance}), the
actual paths do \emph{not} contain a double \texttt{binance/binance}
segment. The comment is slightly misleading; the actual path produced
for extracted klines is:
\begin{lstlisting}
C:\Courses\thesis_AMM\data_raw\CEX\binance\spot\<granularity>\klines\<SYM>\<INT>\
\end{lstlisting}

\subsection{Period Iterators}

\begin{itemize}
  \item \texttt{iter\_days(start\_date, end\_date)} --- yields
        \texttt{date} objects from \texttt{start\_date} to
        \texttt{end\_date} inclusive (one per calendar day).
  \item \texttt{iter\_months(start\_date, end\_date)} --- yields
        \texttt{"YYYY-MM"} strings from the month of
        \texttt{start\_date} to the month of \texttt{end\_date}
        inclusive (one per calendar month).
  \item \texttt{periods\_for\_granularity(...)} --- dispatches to the
        correct iterator and returns a \texttt{list[str]}.
\end{itemize}

Both iterators raise \texttt{ValueError} if \texttt{end\_date <
start\_date}.

\subsection{ZIP Download and Retry}

\texttt{download\_zip} downloads to a temporary file
\texttt{<name>.zip.tmp} and atomically renames it to \texttt{<name>.zip}
on success. This prevents corrupt partial files from being mistaken
for completed downloads. Key behaviours:

\begin{itemize}
  \item A 404 response is returned immediately as
        \texttt{missing\_404} without retrying.
  \item A zero-byte download sets \texttt{last\_error} and retries.
  \item Any other exception (timeout, connection error, non-404
        HTTP error) is caught, stored in \texttt{last\_error}, and
        retried up to \texttt{MAX\_RETRIES = 3} times with a fixed
        \texttt{RETRY\_SLEEP\_SECONDS = 2.0} second pause between
        attempts. The retry wait is \emph{not} exponential.
  \item The \texttt{.tmp} file is deleted on exhaustion.
\end{itemize}

\subsection{CSV Extraction}

\texttt{extract\_zip\_csv} opens the ZIP with
\texttt{zipfile.ZipFile} and extracts all members whose names end in
\texttt{.csv} (case-insensitive). Existing files are skipped unless
\texttt{overwrite=True}. The raw CSV content is written exactly as
found in the archive; no column names or type conversions are applied.

\subsection{SHA-256 Hashing}

\texttt{sha256\_file} reads the ZIP file in 1~MiB blocks and
returns the hexadecimal SHA-256 digest. This digest is stored in the
manifest and can be used to verify that a local archive has not been
corrupted or altered since download. The hash is computed on the
\emph{ZIP file}, not on the extracted CSV.

\subsection{Manifest Writer}

\texttt{append\_manifest\_row} appends one row to
\texttt{output\_root / "download\_manifest.csv"}. The file is created
with a header on first write (detected by checking whether the file
exists). The \texttt{timestamp\_utc} field is set to
\texttt{datetime.now(timezone.utc).replace(microsecond=0).isoformat()},
i.e.\ a second-resolution ISO-8601 UTC string, at the time the row is
written --- which is after download, extraction, and hashing, not at
the time the HTTP request was issued.

% ============================================================
\section{Main Controller: \texttt{main\_import\_cex.py}}
\label{sec:main}

\subsection{Purpose}

\texttt{main\_import\_cex.py} is the recommended entry point. All
user parameters are centralised here; individual fetch scripts need
not be edited. The script builds a configuration dictionary from the
module-level constants, applies optional CLI overrides, then calls
\texttt{download\_binance\_klines}, \texttt{download\_binance\_agg\_trades},
and (optionally) \texttt{collect\_orderbook\_snapshots}.

\subsection{Default Test Parameters}

The module-level constants are deliberately small to allow a fast
test before running the full import.

\begin{xltabular}{\linewidth}{L{4.8cm}L{3.0cm}Y}
\toprule
\textbf{Constant} & \textbf{Default value} & \textbf{Meaning} \\
\midrule
\texttt{OUTPUT\_ROOT} & \texttt{BINANCE\_OUTPUT\_ROOT} &
  Binance raw-data output directory (from \texttt{cex\_config.py}). \\
\texttt{START\_DATE} & \texttt{"2024-01-01"} &
  First date to import. \\
\texttt{END\_DATE} & \texttt{"2024-01-02"} &
  Last date; inclusive for daily files. \\
\texttt{ARCHIVE\_GRANULARITY} & \texttt{"daily"} &
  Use daily Binance public-data archives. \\
\texttt{SYMBOLS} & \texttt{["ETHUSDC"]} &
  Symbol list for the test import. \\
\texttt{INTERVALS} & \texttt{["1m", "5m"]} &
  Kline intervals to download. \\
\texttt{DOWNLOAD\_KLINES} & \texttt{True} &
  Download historical kline files. \\
\texttt{DOWNLOAD\_AGG\_TRADES} & \texttt{True} &
  Download historical aggregate-trade files. \\
\texttt{EXTRACT\_ZIP} & \texttt{True} &
  Extract CSV from downloaded ZIPs. \\
\texttt{KEEP\_ZIP} & \texttt{True} &
  Retain original ZIP archives. \\
\texttt{OVERWRITE} & \texttt{False} &
  Skip files that already exist locally. \\
\texttt{SLEEP\_BETWEEN\_DOWNLOADS\_SECONDS} &
  \texttt{DEFAULT\_SLEEP\_ BETWEEN\_DOWNLOADS\_ SECONDS} &
  Inherited from \texttt{cex\_config.py}: 0.25 seconds. \\
\texttt{COLLECT\_LIVE\_ORDERBOOK} & \texttt{False} &
  Order-book collection is disabled by default. \\
\texttt{ORDERBOOK\_SYMBOLS} & \texttt{["ETHUSDC"]} &
  Symbols for live order-book collection. \\
\texttt{ORDERBOOK\_SECONDS} & \texttt{60} &
  Collect for 60 seconds; 0 means run until \texttt{Ctrl+C}. \\
\texttt{ORDERBOOK\_INTERVAL\_SEC} & \texttt{10.0} &
  Target polling interval in seconds. \\
\texttt{ORDERBOOK\_LIMIT} & \texttt{1000} &
  Maximum bid/ask levels requested from the REST endpoint. \\
\texttt{ORDERBOOK\_DEPTH\_BPS} & \texttt{[1, 5, 10, 50]} &
  Basis-point thresholds for depth aggregation. \\
\texttt{ORDERBOOK\_SAVE\_FULL\_SNAPSHOTS} & \texttt{True} &
  Save full NDJSON snapshots in addition to CSV summaries. \\
\bottomrule
\end{xltabular}

Default test command (small ETHUSDC import, 2024-01-01 to 2024-01-02):
\begin{lstlisting}
python scripts\import_data\CEX\main_import_cex.py
\end{lstlisting}

\subsection{Full-History Preset}

Activated by \texttt{--full-history}. The preset is defined in
\texttt{apply\_full\_history\_preset()} and returns a dictionary that
\texttt{cfg.update()} merges into the base configuration, overriding
only the keys listed:

\begin{xltabular}{\linewidth}{L{3.8cm}L{3.0cm}Y}
\toprule
\textbf{Key} & \textbf{Value} & \textbf{Notes} \\
\midrule
\texttt{start\_date} & \texttt{"2022-01-01"} &
  Extended sample start. \\
\texttt{end\_date} & \texttt{"2026-04-30"} &
  Thesis data cut. \\
\texttt{granularity} & \texttt{"monthly"} &
  Monthly archives to avoid thousands of daily requests. \\
\texttt{symbols} & \texttt{["ETHUSDC", "ETHUSDT", "USDCUSDT"]} &
  Full symbol set. ETHUSDC files before its Binance launch date
  will return \texttt{missing\_404}. \\
\texttt{intervals} & \texttt{["1m", "5m"]} &
  Unchanged from defaults. \\
\texttt{download\_klines} & \texttt{True} & \\
\texttt{download\_agg\_trades} & \texttt{True} & \\
\bottomrule
\end{xltabular}

All other keys (\texttt{extract\_zip}, \texttt{keep\_zip},
\texttt{overwrite}, \texttt{sleep\_between\_downloads\_seconds},
all \texttt{orderbook\_*}) retain their module-level defaults unless
separately overridden by CLI arguments.

Recommended full-history command (from project root):
\begin{lstlisting}
python scripts\import_data\run_cex.py
\end{lstlisting}
Alternatively, invoke \texttt{main\_import\_cex.py} directly:
\begin{lstlisting}
python scripts\import_data\CEX\main_import_cex.py --full-history
\end{lstlisting}

\subsection{Command-Line Overrides}

CLI arguments are parsed by \texttt{apply\_cli\_overrides}. They take
effect after the preset (if \texttt{--full-history} is set), so a CLI
override can further narrow the full-history preset.

\begin{xltabular}{\linewidth}{L{5.0cm}Y}
\toprule
\textbf{Argument} & \textbf{Effect} \\
\midrule
\texttt{--full-history} &
  Apply the full-history preset before any other overrides. \\
\texttt{--start YYYY-MM-DD} & Override \texttt{start\_date}. \\
\texttt{--end YYYY-MM-DD} & Override \texttt{end\_date}. For daily
  files, \texttt{end\_date} is inclusive. \\
\texttt{--granularity daily|monthly} & Override archive granularity. \\
\texttt{--symbols A,B,C} & Override symbol list (comma-separated). \\
\texttt{--intervals 1m,5m} & Override kline intervals
  (comma-separated). \\
\texttt{--output-root PATH} & Override \texttt{output\_root}. \\
\texttt{--no-klines} & Set \texttt{download\_klines = False}. \\
\texttt{--no-agg-trades} & Set \texttt{download\_agg\_trades = False}. \\
\texttt{--overwrite} & Set \texttt{overwrite = True}. \\
\texttt{--no-extract} & Set \texttt{extract\_zip = False}. \\
\texttt{--delete-zip-after-extract} & Set \texttt{keep\_zip = False}.
  Deletes each ZIP after extracting its CSV. Not recommended because
  it removes the SHA-256-verifiable source archive. \\
\texttt{--collect-orderbook} & Set \texttt{collect\_live\_orderbook
  = True}. \\
\bottomrule
\end{xltabular}

% ============================================================
\section{Historical Klines: \texttt{fetch\_binance\_klines.py}}
\label{sec:klines}

\subsection{Download Logic}

\texttt{download\_binance\_klines} iterates over the Cartesian product
of symbols $\times$ intervals $\times$ periods and calls
\texttt{download\_one\_binance\_public\_file} for each triple. Symbols
and intervals are normalised to uppercase/stripped before use.
The function returns a list of \texttt{DownloadResult} objects.

Direct invocation example:
\begin{lstlisting}
python scripts\import_data\CEX\fetch_binance_klines.py ^
  --symbols ETHUSDC ^
  --intervals 1m,5m ^
  --start 2024-01-01 ^
  --end 2024-01-02 ^
  --granularity daily
\end{lstlisting}

\subsection{Output Paths}

\begin{lstlisting}
# Extracted CSV
C:\...\data_raw\CEX\binance\spot\<gran>\klines\<SYM>\<INT>\<SYM>-<INT>-<PERIOD>.csv

# ZIP archive
C:\...\data_raw\CEX\binance\zip_archives\spot\<gran>\klines\<SYM>\<INT>\<SYM>-<INT>-<PERIOD>.zip
\end{lstlisting}

\subsection{Raw Kline CSV Format}

Raw klines CSV files have \textbf{no header row}. The 12 columns must
be assigned names from \texttt{KLINE\_COLUMNS} in the processing
stage. All numeric fields are stored as decimal strings by Binance
and should be cast to \texttt{float64} during processing.

\begin{xltabular}{\linewidth}{L{4.8cm}L{2.8cm}Y}
\toprule
\textbf{Column name} & \textbf{Raw type} & \textbf{Description} \\
\midrule
\texttt{open\_time\_ms} & Integer string &
  UTC open time of the kline in milliseconds since Unix epoch.
  Divide by 1000 to obtain seconds; use
  \texttt{pd.to\_datetime(..., unit="ms", utc=True)} for conversion. \\
\texttt{open} & Decimal string &
  Opening price. \\
\texttt{high} & Decimal string &
  Highest traded price during the interval. \\
\texttt{low} & Decimal string &
  Lowest traded price during the interval. \\
\texttt{close} & Decimal string &
  Closing price. Baseline candidate for $p_t^{*}$ in simple
  processing. \\
\texttt{volume\_base} & Decimal string &
  Total base-asset volume during the interval. For ETHUSDC and
  ETHUSDT, this is ETH quantity. \\
\texttt{close\_time\_ms} & Integer string &
  UTC close time in milliseconds. Equal to
  \texttt{open\_time\_ms} $+$ interval duration $-$ 1 ms. \\
\texttt{quote\_asset\_volume} & Decimal string &
  Total quote-asset volume. For ETHUSDC: USDC; for ETHUSDT: USDT.
  Used to construct $Q_t^{\mathrm{CEX}}$. \\
\texttt{number\_of\_trades} & Integer string &
  Number of trades during the interval. Proxy for
  $N_t^{\mathrm{CEX}}$. \\
\texttt{taker\_buy\_base\_volume} & Decimal string &
  Base-asset volume from taker buy orders. Useful for signed
  order-flow proxies. \\
\texttt{taker\_buy\_quote\_volume} & Decimal string &
  Quote-asset volume from taker buy orders. \\
\texttt{ignore} & String &
  Binance-provided unused field. Drop during processing. \\
\bottomrule
\end{xltabular}

\subsection{Model Objects Constructed from Klines}

\begin{align*}
  p_t^{*} &= \text{CEX reference price (close, mid, or VWAP)}, \\
  r_t &= \log p_t^{*} - \log p_{t-1}^{*}, \\
  \sigma_t^{(1\mathrm{m})} &=
    \sqrt{1440}\;\mathrm{sd}\!\left(r_{t-1439},\ldots,r_t\right)
    \quad\text{(1-min daily realised volatility)},\\
  \sigma_t^{(5\mathrm{m})} &=
    \sqrt{288}\;\mathrm{sd}\!\left(r_{t-287},\ldots,r_t\right)
    \quad\text{(5-min daily realised volatility)},\\
  Q_t^{\mathrm{CEX}} &= \texttt{quote\_asset\_volume}, \\
  N_t^{\mathrm{CEX}} &= \texttt{number\_of\_trades}.
\end{align*}

The square-root scaling assumes i.i.d.\ returns over the interval
and converts the per-interval standard deviation to a daily measure.
A more robust estimator (e.g.\ Parkinson or Garman--Klass using the
high and low fields) can be constructed in the processing stage.

% ============================================================
\section{Historical Aggregate Trades: \texttt{fetch\_binance\_agg\_trades.py}}
\label{sec:aggtrades}

\subsection{Download Logic}

\texttt{download\_binance\_agg\_trades} iterates over symbols
$\times$ periods (no interval dimension). Otherwise the logic is
identical to the kline downloader.

Direct invocation example:
\begin{lstlisting}
python scripts\import_data\CEX\fetch_binance_agg_trades.py ^
  --symbols ETHUSDC ^
  --start 2024-01-01 ^
  --end 2024-01-02 ^
  --granularity daily
\end{lstlisting}

\subsection{Output Paths}

\begin{lstlisting}
# Extracted CSV
C:\...\data_raw\CEX\binance\spot\<gran>\aggTrades\<SYM>\<SYM>-aggTrades-<PERIOD>.csv

# ZIP archive
C:\...\data_raw\CEX\binance\zip_archives\spot\<gran>\aggTrades\<SYM>\<SYM>-aggTrades-<PERIOD>.zip
\end{lstlisting}

\subsection{What Is an Aggregate Trade?}

A Binance aggregate trade is a record in which all individual raw
fills from a single taker order that were matched at the same price
within the same millisecond are compressed into one entry. The number
of raw fills compressed is \texttt{last\_trade\_id} $-$
\texttt{first\_trade\_id} $+$ 1. When a taker order is matched across
multiple price levels or milliseconds, it produces multiple aggregate
trade records.

This differs from a kline in that aggregate trades preserve
sub-interval granularity and individual transaction prices, but
differs from the raw matching-engine feed in that fine-grained fills
at the same price and millisecond are collapsed. Aggregate trades are
not uniquely attributed to individual users.

\subsection{Raw Aggregate-Trade CSV Format}

Raw aggregate-trade CSV files have \textbf{no header row}. Assign
names from \texttt{AGG\_TRADE\_COLUMNS} during processing.

\begin{xltabular}{\linewidth}{L{4.2cm}L{2.8cm}Y}
\toprule
\textbf{Column name} & \textbf{Raw type} & \textbf{Description} \\
\midrule
\texttt{agg\_trade\_id} & Integer string &
  Monotonically increasing aggregate-trade identifier for the symbol.
  Use for deduplication and ordering when combining files. \\
\texttt{price} & Decimal string &
  Transaction price in quote-asset units. \\
\texttt{quantity} & Decimal string &
  Traded quantity in base-asset units. For ETH pairs, this is ETH. \\
\texttt{first\_trade\_id} & Integer string &
  First underlying raw-trade ID compressed into this aggregate. \\
\texttt{last\_trade\_id} & Integer string &
  Last underlying raw-trade ID. The number of underlying fills is
  \texttt{last\_trade\_id} $-$ \texttt{first\_trade\_id} $+$ 1. \\
\texttt{transact\_time\_ms} & Integer string &
  Transaction timestamp in milliseconds since Unix epoch (UTC).
  Use for time-bucketing and CEX--DEX alignment. \\
\texttt{is\_buyer\_maker} & Boolean string &
  \texttt{True} if the buyer was the maker (i.e.\ the seller was
  the aggressor/taker). A taker sell corresponds to
  \texttt{is\_buyer\_maker = True}; a taker buy corresponds to
  \texttt{is\_buyer\_maker = False}. \\
\texttt{is\_best\_match} & Boolean string &
  Exchange-provided match-quality flag. Typically \texttt{True} for
  all records in the downloaded files; retain and check during
  processing. \\
\bottomrule
\end{xltabular}

\paragraph{Trade direction convention.}
The \texttt{is\_buyer\_maker} field follows the Binance convention:
\begin{align*}
  \texttt{is\_buyer\_maker} = \texttt{True}
  &\;\Rightarrow\; \text{seller was the taker (aggressive sell)},\\
  \texttt{is\_buyer\_maker} = \texttt{False}
  &\;\Rightarrow\; \text{buyer was the taker (aggressive buy)}.
\end{align*}
Signed order flow (positive = net buy) can be constructed during
processing as:
$\delta_i = (+q_i)$ if \texttt{is\_buyer\_maker} $=$ \texttt{False},
else $\delta_i = (-q_i)$.

\subsection{Model Objects Constructed from Aggregate Trades}

For interval $t$:
\begin{align*}
  N_t^{\mathrm{CEX}} &=
    \#\{\text{aggregate trades with }
    \texttt{transact\_time\_ms} \in t\}, \\
  Q_t^{\mathrm{CEX}} &= \sum_{i \in t} p_i\, q_i, \\
  \bar{q}_t^{\mathrm{CEX}} &=
    \frac{Q_t^{\mathrm{CEX}}}{N_t^{\mathrm{CEX}}}, \\
  p_t^{\mathrm{VWAP}} &=
    \frac{\sum_{i \in t} p_i\, q_i}{\sum_{i \in t} q_i}, \\
  \Delta_t^{\mathrm{CEX}} &=
    \sum_{i \in t} \delta_i
    \quad \text{(signed net order flow in base-asset units)}.
\end{align*}

% ============================================================
\section{Live Order-Book Collector:
  \texttt{collect\_binance\_orderbook\_rest.py}}
\label{sec:orderbook}

\subsection{Purpose and Scope}

This script polls the Binance REST depth endpoint
(\texttt{GET /api/v3/depth}) at a configurable interval. It is a
\emph{prospective} collector: it records snapshots from the moment
it is started and does not backfill historical order-book state.
For the thesis, it provides bid--ask spreads and order-book depth
going forward from the date of collection.

\subsection{Polling Logic and Timing}

For each polling cycle, the script:
\begin{enumerate}
  \item Records \texttt{loop\_start = time.monotonic()}.
  \item For each symbol, calls \texttt{fetch\_depth} (with up to 3
        retries and a hard-coded 2.0-second sleep between retries,
        independent of \texttt{RETRY\_SLEEP\_SECONDS}).
  \item Appends the compact summary row to the daily CSV.
  \item Optionally appends the full snapshot to the daily NDJSON.
  \item Computes \texttt{elapsed = time.monotonic() - loop\_start}
        and sleeps \texttt{max(0, interval\_sec - elapsed)} seconds.
\end{enumerate}

The cycle time is therefore bounded below by the HTTP latency and
above by \texttt{interval\_sec} (default 10.0 seconds). If processing
all symbols takes longer than \texttt{interval\_sec}, the next cycle
starts immediately with no sleep. Timestamps in the output files
reflect the \emph{local system clock} at the time each snapshot is
processed, not the server time embedded in the REST response.

The script runs until \texttt{seconds} have elapsed (\texttt{seconds
= 0} means run indefinitely until \texttt{Ctrl+C}
(\texttt{KeyboardInterrupt})).

\subsection{Output Paths}

\begin{lstlisting}
C:\...\data_raw\CEX\binance\live_orderbook\<SYM>\depth_summary_YYYYMMDD.csv
C:\...\data_raw\CEX\binance\live_orderbook\<SYM>\depth_snapshots_YYYYMMDD.ndjson
\end{lstlisting}

The date key (\texttt{YYYYMMDD}) is computed from
\texttt{datetime.now(timezone.utc)} at the start of each polling cycle.
If the collector runs across a UTC midnight, a new daily file is started
automatically.

\subsection{Depth Computation}

The \texttt{summarize\_depth} function extracts the best bid and ask
from the first element of the returned bid and ask arrays (already
sorted best-first by Binance), computes the midprice and spread, and
then calls \texttt{notional\_depth\_within\_bps} for each threshold
$b \in \{1, 5, 10, 50\}$.

The depth filter is:
\begin{align*}
  \mathcal{B}_t(b) &= \left\{ j : p_j^{\mathrm{bid}} \geq
    p_t^{\mathrm{mid}}\!\left(1 - \tfrac{b}{10000}\right) \right\}, \\
  \mathcal{A}_t(b) &= \left\{ j : p_j^{\mathrm{ask}} \leq
    p_t^{\mathrm{mid}}\!\left(1 + \tfrac{b}{10000}\right) \right\}.
\end{align*}

The quote-asset notional depth is:
\[
  D_t^{\mathrm{bid}}(b) =
    \sum_{j \in \mathcal{B}_t(b)} p_j^{\mathrm{bid}}\, q_j^{\mathrm{bid}},
  \qquad
  D_t^{\mathrm{ask}}(b) =
    \sum_{j \in \mathcal{A}_t(b)} p_j^{\mathrm{ask}}\, q_j^{\mathrm{ask}}.
\]

The spread is:
\[
  s_t^{\mathrm{abs}} = p_t^{\mathrm{ask}} - p_t^{\mathrm{bid}},
  \qquad
  s_t^{\mathrm{bps}} = \frac{10000 \cdot s_t^{\mathrm{abs}}}
    {p_t^{\mathrm{mid}}}.
\]

$s_t^{\mathrm{bps}}$ is set to \texttt{None} (and written as an empty
field in the CSV) if $p_t^{\mathrm{mid}} = 0$.

\subsection{Compact CSV Summary Format}

Written to \texttt{depth\_summary\_YYYYMMDD.csv} (one row per
snapshot per symbol). The CSV has a header row written on first
creation.

\begin{xltabular}{\linewidth}{L{4.8cm}L{2.4cm}Y}
\toprule
\textbf{Column name} & \textbf{Type} & \textbf{Description} \\
\midrule
\texttt{timestamp\_utc} & ISO string &
  UTC timestamp at which the row was written (second resolution,
  from \texttt{utc\_now\_iso()}). Reflects local processing time,
  not server time. \\
\texttt{exchange} & string &
  Always \texttt{"binance"}. \\
\texttt{symbol} & string &
  Trading pair, e.g.\ \texttt{"ETHUSDC"} (upper-stripped). \\
\texttt{last\_update\_id} & integer &
  Binance order-book update ID from the REST response
  (\texttt{lastUpdateId}). Can be used to detect missed updates. \\
\texttt{best\_bid} & float &
  \texttt{float(bids[0][0])}: the highest bid price returned. \\
\texttt{best\_ask} & float &
  \texttt{float(asks[0][0])}: the lowest ask price returned. \\
\texttt{mid\_price} & float &
  $(\texttt{best\_bid} + \texttt{best\_ask}) / 2$. \\
\texttt{spread\_abs} & float &
  $\texttt{best\_ask} - \texttt{best\_bid}$. \\
\texttt{spread\_bps} & float/None &
  $10000 \times \texttt{spread\_abs} / \texttt{mid\_price}$.
  \texttt{None} if midprice is zero. \\
\texttt{bid\_levels\_returned} & integer &
  Length of the \texttt{bids} array in the REST response. At most
  \texttt{limit} levels (default 1000). \\
\texttt{ask\_levels\_returned} & integer &
  Length of the \texttt{asks} array. \\
\texttt{bid\_depth\_quote\_1bps} & float &
  $D_t^{\mathrm{bid}}(1)$. \\
\texttt{ask\_depth\_quote\_1bps} & float &
  $D_t^{\mathrm{ask}}(1)$. \\
\texttt{bid\_depth\_quote\_5bps} & float &
  $D_t^{\mathrm{bid}}(5)$. \\
\texttt{ask\_depth\_quote\_5bps} & float &
  $D_t^{\mathrm{ask}}(5)$. \\
\texttt{bid\_depth\_quote\_10bps} & float &
  $D_t^{\mathrm{bid}}(10)$. \\
\texttt{ask\_depth\_quote\_10bps} & float &
  $D_t^{\mathrm{ask}}(10)$. \\
\texttt{bid\_depth\_quote\_50bps} & float &
  $D_t^{\mathrm{bid}}(50)$. \\
\texttt{ask\_depth\_quote\_50bps} & float &
  $D_t^{\mathrm{ask}}(50)$. \\
\bottomrule
\end{xltabular}

\subsection{Full Snapshot NDJSON Format}

Written to \texttt{depth\_snapshots\_YYYYMMDD.ndjson}. Each line is
one JSON object (no trailing comma; files are opened in append mode).

\begin{xltabular}{\linewidth}{L{3.6cm}Y}
\toprule
\textbf{Field} & \textbf{Description} \\
\midrule
\texttt{timestamp\_utc} & ISO UTC timestamp (same value as in the
  summary CSV row). \\
\texttt{exchange} & Always \texttt{"binance"}. \\
\texttt{symbol} & Trading pair. \\
\texttt{depth\_limit} & The \texttt{limit} parameter passed to the
  REST request (default 1000). \\
\texttt{depth} & Raw JSON response body: a dict with
  \texttt{lastUpdateId} (integer), \texttt{bids} (list of
  [\textit{price\_str}, \textit{qty\_str}] pairs, best-first),
  and \texttt{asks} (list of [\textit{price\_str},
  \textit{qty\_str}] pairs, best-first). \\
\bottomrule
\end{xltabular}

\subsection{Using the Collector from Main}

When \texttt{COLLECT\_LIVE\_ORDERBOOK = True} in
\texttt{main\_import\_cex.py}, the controller calls
\texttt{collect\_orderbook\_snapshots} with the parameters
\texttt{ORDERBOOK\_SYMBOLS}, \texttt{ORDERBOOK\_SECONDS},
\texttt{ORDERBOOK\_INTERVAL\_SEC}, \texttt{ORDERBOOK\_LIMIT},
\texttt{ORDERBOOK\_DEPTH\_BPS}, and
\texttt{ORDERBOOK\_SAVE\_FULL\_SNAPSHOTS}. The collector runs
after all historical downloads complete. To run the collector
independently without downloading historical files, use:

\begin{lstlisting}
python scripts\import_data\CEX\collect_binance_orderbook_rest.py ^
  --symbols ETHUSDC,ETHUSDT ^
  --seconds 0 ^
  --interval-sec 10 ^
  --limit 1000 ^
  --depth-bps 1,5,10,50
\end{lstlisting}

% ============================================================
\section{Manifest File}
\label{sec:manifest}

\begin{lstlisting}
C:\Courses\thesis_AMM\data_raw\CEX\binance\download_manifest.csv
\end{lstlisting}

Every call to \texttt{download\_one\_binance\_public\_file} appends
exactly one row. The manifest is the central reproducibility file for
the CEX import. It is written by \texttt{append\_manifest\_row} in
\texttt{binance\_download\_utils.py}.

\begin{xltabular}{\linewidth}{L{4.0cm}Y}
\toprule
\textbf{Column name} & \textbf{Description} \\
\midrule
\texttt{timestamp\_utc} &
  ISO-8601 UTC timestamp (second resolution) at which the manifest
  row was written. This is after download, extraction, and hashing
  have completed, not the HTTP request time. \\
\texttt{exchange} & Always \texttt{"binance"}. \\
\texttt{market\_type} & Always \texttt{"spot"}. \\
\texttt{data\_type} & \texttt{"klines"} or \texttt{"aggTrades"}. \\
\texttt{symbol} & Trading pair, uppercase. \\
\texttt{interval} & Kline interval (\texttt{"1m"}, \texttt{"5m"}, etc.).
  Empty string for aggTrades. \\
\texttt{granularity} & \texttt{"daily"} or \texttt{"monthly"}. \\
\texttt{period} & \texttt{YYYY-MM-DD} (daily) or \texttt{YYYY-MM}
  (monthly). \\
\texttt{url} & Full remote URL requested. \\
\texttt{zip\_path} & Absolute local path of the ZIP archive. \\
\texttt{extracted\_dir} & Directory where CSV was extracted. Empty
  string when \texttt{extracted\_dir} is \texttt{None} in the
  \texttt{DownloadResult}. \\
\texttt{status} & One of the status values in
  Section~\ref{sec:statuses}. \\
\texttt{bytes\_downloaded} & Bytes written or file size. 0 for
  \texttt{missing\_404} and \texttt{failed}. \\
\texttt{sha256} & Hex SHA-256 digest of the local ZIP. Empty string
  when the file was not written or available. \\
\texttt{error} & Error message. Empty string when no error. \\
\bottomrule
\end{xltabular}

% ============================================================
\section{Full Output Directory Structure}
\label{sec:structure}

\textbf{After the default test import}
(\texttt{ETHUSDC}, daily, 2024-01-01 to 2024-01-02):

\begin{lstlisting}
data_raw\CEX\binance\
    download_manifest.csv
    spot\daily\klines\ETHUSDC\1m\ETHUSDC-1m-2024-01-01.csv
                                 ETHUSDC-1m-2024-01-02.csv
                          \5m\ETHUSDC-5m-2024-01-01.csv
                                 ETHUSDC-5m-2024-01-02.csv
    spot\daily\aggTrades\ETHUSDC\ETHUSDC-aggTrades-2024-01-01.csv
                                 ETHUSDC-aggTrades-2024-01-02.csv
    zip_archives\spot\daily\klines\ETHUSDC\1m\*.zip
                                          \5m\*.zip
    zip_archives\spot\daily\aggTrades\ETHUSDC\*.zip
\end{lstlisting}

\textbf{After the full-history import}
(\texttt{ETHUSDC}, \texttt{ETHUSDT}, \texttt{USDCUSDT},
monthly, 2022-01 to 2026-04):

\begin{lstlisting}
data_raw\CEX\binance\
    download_manifest.csv
    spot\monthly\klines\ETHUSDC\1m\*.csv
                               \5m\*.csv
    spot\monthly\klines\ETHUSDT\1m\*.csv
                               \5m\*.csv
    spot\monthly\klines\USDCUSDT\1m\*.csv
                                \5m\*.csv
    spot\monthly\aggTrades\ETHUSDC\*.csv
    spot\monthly\aggTrades\ETHUSDT\*.csv
    spot\monthly\aggTrades\USDCUSDT\*.csv
    zip_archives\spot\monthly\klines\...
    zip_archives\spot\monthly\aggTrades\...
\end{lstlisting}

\textbf{Live order-book output} (if collector is activated):

\begin{lstlisting}
data_raw\CEX\binance\
    live_orderbook\ETHUSDC\depth_summary_YYYYMMDD.csv
                          \depth_snapshots_YYYYMMDD.ndjson
    live_orderbook\ETHUSDT\depth_summary_YYYYMMDD.csv
                          \depth_snapshots_YYYYMMDD.ndjson
\end{lstlisting}

% ============================================================
\section{Imported Data to Model Calibration Objects}
\label{sec:use}

\begin{xltabular}{\linewidth}{L{3.0cm}L{3.8cm}Y}
\toprule
\textbf{Model object} & \textbf{Raw source} & \textbf{Construction} \\
\midrule
$p_t^{*}$ &
  Klines or agg trades &
  Use kline \texttt{close}, mid-interval price, or aggregate-trade
  VWAP as the external CEX reference price. \\
$r_t$ &
  $p_t^{*}$ &
  $\log p_t^{*} - \log p_{t-1}^{*}$. \\
$\sigma_t$ &
  Klines &
  Realised volatility from scaled standard deviation of
  $r_t$; or Parkinson/Garman--Klass using \texttt{high} and
  \texttt{low}. \\
$Q_t^{\mathrm{CEX}}$ &
  Klines or agg trades &
  \texttt{quote\_asset\_volume} from klines, or
  $\sum_{i \in t} p_i q_i$ from aggregate trades. \\
$N_t^{\mathrm{CEX}}$ &
  Klines or agg trades &
  \texttt{number\_of\_trades} from klines, or count of aggregate
  trade rows by interval. \\
$\bar{q}_t^{\mathrm{CEX}}$ &
  Agg trades &
  $Q_t^{\mathrm{CEX}} / N_t^{\mathrm{CEX}}$. \\
$p_t^{\mathrm{VWAP}}$ &
  Agg trades &
  $\sum_{i \in t} p_i q_i / \sum_{i \in t} q_i$. \\
$\Delta_t^{\mathrm{CEX}}$ &
  Agg trades &
  Signed net order flow: $\sum_{i \in t} \delta_i$ where
  $\delta_i = +q_i$ if \texttt{is\_buyer\_maker = False},
  else $-q_i$. \\
$s_t$ &
  Order-book summary &
  \texttt{spread\_bps} or
  $\texttt{spread\_abs} / \texttt{mid\_price}$. \\
$D_t^{\mathrm{CEX}}(b)$ &
  Order-book summary &
  $D_t^{\mathrm{bid}}(b)$ or $D_t^{\mathrm{ask}}(b)$ for
  $b \in \{1, 5, 10, 50\}$ bp. \\
$p_t^{\mathrm{ETH/USDC}}$ (synthetic) &
  ETHUSDT $+$ USDCUSDT klines or agg trades &
  $p_t^{\mathrm{ETH/USDT}} / p_t^{\mathrm{USDC/USDT}}$;
  used to extend the USDC-denominated benchmark before ETHUSDC
  was available on Binance. \\
$d_t$ &
  DEX AMM price $+$ $p_t^{*}$ &
  $(p_t^{\mathrm{AMM}} - p_t^{*}) / p_t^{*}$; computed after
  merging with the DEX data. \\
\bottomrule
\end{xltabular}

% ============================================================
\section{Quality Checks}
\label{sec:qc}

After import and before processing:

\begin{enumerate}
  \item \textbf{Manifest completeness.}
        Confirm \texttt{download\_manifest.csv} has one row per
        (symbol, interval/data-type, period) combination. Count
        \texttt{missing\_404} rows and record the set of unavailable
        symbol-period pairs.

  \item \textbf{Expected file count.}
        For the full-history monthly import:
        count rows with status containing \texttt{extracted} and
        verify the count equals
        (3 symbols $\times$ 2 intervals $\times$ 52 months) for
        klines plus (3 symbols $\times$ 52 months) for aggTrades,
        less any \texttt{missing\_404} rows.

  \item \textbf{SHA-256 integrity.}
        Re-hash each local ZIP and compare against the manifest
        \texttt{sha256} field to detect post-download corruption.

  \item \textbf{CSV column count.}
        Read each extracted CSV and verify it has exactly 12 columns
        (klines) or 8 columns (aggregate trades).

  \item \textbf{No-header check.}
        Confirm the first row of each CSV is numeric, not a header
        string (Binance public-data files vary in this respect for
        some symbols/periods).

  \item \textbf{Timestamp monotonicity.}
        For klines: verify \texttt{open\_time\_ms} is strictly
        increasing within each file. For aggregate trades: verify
        \texttt{agg\_trade\_id} is strictly increasing and
        \texttt{transact\_time\_ms} is non-decreasing.

  \item \textbf{No inter-file gaps or overlaps.}
        For klines: the \texttt{open\_time\_ms} of the first row in
        file $m{+}1$ should equal the \texttt{close\_time\_ms} of the
        last row in file $m$ plus 1 millisecond.

  \item \textbf{No inter-file duplicate agg trade IDs.}
        When combining monthly aggregate-trade files, verify that
        \texttt{agg\_trade\_id} values across consecutive files do not
        overlap.

  \item \textbf{Price sanity.}
        Check that \texttt{low} $\leq$ \texttt{open},
        \texttt{close} $\leq$ \texttt{high} for every kline row.

  \item \textbf{Volume non-negativity.}
        Confirm \texttt{volume\_base}, \texttt{quote\_asset\_volume},
        \texttt{taker\_buy\_base\_volume}, and
        \texttt{taker\_buy\_quote\_volume} are non-negative.

  \item \textbf{USDC depeg window.}
        Flag rows where \texttt{open\_time\_ms} or
        \texttt{transact\_time\_ms} falls between approximately
        2023-03-10 and 2023-03-13 UTC. During this period, USDC
        briefly traded below \$1.00. All ETHUSDC prices and
        USDC/USDT cross-rates in this window reflect non-par USDC.

  \item \textbf{Order-book timestamp alignment.}
        Confirm that \texttt{timestamp\_utc} values in the live
        order-book CSV are within the expected collection window and
        that inter-snapshot gaps are approximately
        \texttt{ORDERBOOK\_INTERVAL\_SEC} seconds.

  \item \textbf{Spread non-negativity.}
        Confirm \texttt{spread\_abs} $\geq 0$ and \texttt{best\_bid}
        $<$ \texttt{best\_ask} for every order-book row.
\end{enumerate}

% ============================================================
\section{Known Limitations}
\label{sec:limits}

\begin{enumerate}
  \item \textbf{Binance only.}
        The module imports only Binance public data. Coinbase,
        Kraken, and other venues are not implemented.

  \item \textbf{No historical order-book backfill.}
        The order-book collector is prospective. Historical full
        limit-order-book data are not freely available from Binance
        public data and are not collected here.

  \item \textbf{Aggregate trades are not raw fills.}
        The finest granularity available from Binance public data
        is aggregate trades, in which multiple fills at the same
        price and millisecond are collapsed. The number of underlying
        fills is \texttt{last\_trade\_id} $-$ \texttt{first\_trade\_id}
        $+$ 1 and can be used to estimate the compression ratio, but
        individual fill prices are not recoverable.

  \item \textbf{Flat retry wait.}
        \texttt{download\_zip} uses a fixed \texttt{RETRY\_SLEEP\_SECONDS
        = 2.0} second wait between retries, not exponential backoff.
        For transient server-side throttling, this may be insufficient
        to avoid repeated failures. Increasing \texttt{RETRY\_SLEEP\_SECONDS}
        in \texttt{cex\_config.py} is recommended if \texttt{failed}
        rows appear in the manifest.

  \item \textbf{No symbol-availability pre-check.}
        The module does not query Binance for the exchange information
        endpoint before requesting files. Periods before a symbol's
        launch date produce \texttt{missing\_404} entries in the
        manifest; they are not treated as errors.

  \item \textbf{USDC depeg.}
        USDC briefly depegged in March 2023 (approximately
        2023-03-10 to 2023-03-13). All ETHUSDC prices and the
        USDCUSDT cross-rate in this window are measured in non-par
        USDC. Analyses spanning this period should apply a correction
        or exclude the affected dates.

  \item \textbf{No trade-flow classification.}
        The module does not classify aggregate trades as arbitrage,
        market-making, noise flow, or informed trading. Flow
        classification must be performed in the processing stage
        using external reference prices or structural models.

  \item \textbf{Local clock timestamps in order-book data.}
        The \texttt{timestamp\_utc} in order-book output files
        reflects the local system clock at the time the row was
        written, not the server-side time embedded in the Binance
        REST response. Latency between the HTTP request and the
        write operation (typically $<$100 ms) introduces a small
        timing error.

  \item \textbf{Path coupling.}
        \texttt{cex\_config.py} uses \texttt{.parents[3]} to locate
        the project root. Moving any script to a different directory
        depth silently redirects output to a wrong location.

  \item \textbf{No DEX--CEX merge.}
        This module downloads raw CEX inputs only. Merging with
        Uniswap v3 DEX data and computing $d_t$ are deferred to
        \texttt{scripts\textbackslash process\_data\textbackslash CEX}.
\end{enumerate}

% ============================================================
\section{Recommended Processing Stage}
\label{sec:proc}

Processing scripts should be placed in:
\begin{lstlisting}
C:\Courses\thesis_AMM\scripts\process_data\CEX
\end{lstlisting}
and write outputs to:
\begin{lstlisting}
C:\Courses\thesis_AMM\data_processed\CEX
\end{lstlisting}

Recommended processing tasks:
\begin{enumerate}
  \item Read raw kline CSVs with column names from
        \texttt{KLINE\_COLUMNS}; assign header, cast types.
  \item Read raw aggregate-trade CSVs with column names from
        \texttt{AGG\_TRADE\_COLUMNS}.
  \item Convert millisecond timestamps to UTC datetimes:
        \texttt{pd.to\_datetime(col, unit="ms", utc=True)}.
  \item Cast all price and quantity fields from decimal strings to
        \texttt{float64}; cast ID and count fields to \texttt{int64}.
  \item Check for missing periods using the manifest
        \texttt{missing\_404} rows and decide how to handle gaps.
  \item Build 1-minute and 5-minute reference-price panels
        ($p_t^{*}$, $r_t$, $\sigma_t$).
  \item Aggregate trade counts ($N_t^{\mathrm{CEX}}$), volumes
        ($Q_t^{\mathrm{CEX}}$), and average trade sizes
        ($\bar{q}_t^{\mathrm{CEX}}$).
  \item Construct synthetic ETH/USDC from ETHUSDT and USDCUSDT
        where ETHUSDC is unavailable:
        $p^{\mathrm{ETH/USDC}}_t \approx p^{\mathrm{ETH/USDT}}_t
        / p^{\mathrm{USDC/USDT}}_t$.
  \item Merge CEX reference prices with Uniswap v3 WETH/USDC event
        data (nearest-previous or interpolated join by timestamp).
  \item Compute the DEX--CEX deviation:
        $d_t = (p_t^{\mathrm{AMM}} - p_t^{*}) / p_t^{*}$.
  \item Read live order-book CSV summaries; compute spread and
        depth statistics.
  \item Export clean processed panels to
        \texttt{data\_processed\textbackslash CEX}.
\end{enumerate}

% ============================================================
\section{Installation and Execution Checklist}
\label{sec:checklist}

\begin{enumerate}
  \item Place scripts in the correct directories:
        \begin{itemize}
          \item \texttt{run\_cex.py} in
                \path{C:\Courses\thesis_AMM\scripts\import_data}
          \item All other CEX scripts in
                \path{C:\Courses\thesis_AMM\scripts\import_data\CEX}
        \end{itemize}

  \item Install dependencies from the project root:
\begin{lstlisting}
pip install -r requirements.txt
\end{lstlisting}

  \item Run the small test import (from the project root):
\begin{lstlisting}
python scripts\import_data\CEX\main_import_cex.py
\end{lstlisting}
  This downloads ETHUSDC daily klines and aggTrades for
  2024-01-01 to 2024-01-02 only.

  \item Verify outputs:
        \begin{itemize}
          \item \texttt{download\_manifest.csv} exists and has rows
                with status containing \texttt{extracted}.
          \item CSV files exist under
                \path{data_raw\CEX\binance\spot\daily\klines\ETHUSDC\1m}
                and \texttt{5m}.
          \item CSV files exist under
                \path{data_raw\CEX\binance\spot\daily\aggTrades\ETHUSDC}.
          \item ZIP archives exist under
                \path{data_raw\CEX\binance\zip_archives}.
        \end{itemize}

  \item After the test succeeds, run the full historical import:
\begin{lstlisting}
python scripts\import_data\run_cex.py
\end{lstlisting}
  \texttt{run\_cex.py} invokes \texttt{main\_import\_cex.py
  --full-history} and sets \texttt{PYTHONIOENCODING=utf-8}
  for correct console output on Windows. Runtime: 20--60 min.

  \item To collect live order-book data, pass \texttt{--orderbook}
        to the runner:
\begin{lstlisting}
python scripts\import_data\run_cex.py --orderbook
\end{lstlisting}
  Or run the collector independently:
\begin{lstlisting}
python scripts\import_data\CEX\collect_binance_orderbook_rest.py ^
  --symbols ETHUSDC,ETHUSDT --seconds 0 --interval-sec 10
\end{lstlisting}
\end{enumerate}

\end{document}
